Phonon polaritonics in two-dimensional materials

### 2019-03-19 paper.tex
removing a comment

In the rest of this section, we discuss the relation between the dispersion of an hBN monolayer versus the atomically-thick limit of a thin film of a material with hBN's bulk dielectric function. To aid this discussion, in Figure~\ref{fig:2}(c), we show the dispersion relation of thin films of bulk hBN with film thicknesses of 1, 2, 4, and 8 times the interlayer spacing of bulk hBN, which is roughly \SI{0.33}{\nm}. For these plots, we take hBN to be cleaved such that the optical axis is perpendicular to the plane of the film. The components of the bulk permittivity perpendicular and parallel to the c-axis ($\epsilon_{\perp}$ and $\epsilon_{\parallel}$, respectively; indexed by $\alpha\in\{\perp,\parallel\}$ below) are then given by
\begin{equation}
	\epsilon_{\alpha}(\omega) = \epsilon_{\infty,\alpha}\Bigg(1 + \frac{\omega^2_{\mathrm{LO},\alpha}-\omega^2_{\mathrm{TO},\alpha}}{\omega^2_{\mathrm{TO},\alpha}-\omega^2} \Bigg),
	\label{eq:3deps}
\end{equation}
with $\epsilon_{\infty,\parallel} = \num{2.95}$, $\omega_{\mathrm{TO},\parallel} = \SI{760}{\per\cm}$, and $\omega_{\mathrm{LO},\parallel} = \SI{830}{\per\cm}$; and $\epsilon_{\infty,\perp} = \num{4.87}$, $\omega_{\mathrm{TO},\perp} = \SI{1360}{\per\cm}$, and $\omega_{\mathrm{LO},\perp} = \SI{1614}{\per\cm}$\cite{caldwell2014sub,dai2014tunable}.
Losses are ignored in this discussion altogether. 
In the range between $\omega_{\mathrm{TO}, \alpha}$ and $\omega_{\mathrm{LO}, \alpha}$, the corresponding component of the permittivity is negative, while the other component is positive. This hyperbolicity leads to a dispersion for hBN thin films that have multiple branches at a given frequency, as can be seen in Figure~\ref{fig:2}(c).  This trend persists even when the thickness of the bulk is taken down to a single layer, albeit pushed to high wavevectors. This is in contrast with the true monolayer, where there is only one LO phonon mode. Given that the phonon polariton of 2D is the LO phonon, there can be only one branch of the dispersion. 
\addition{%
The bulk dielectric function of Eq.~\eqref{eq:3deps} fails to capture this removal of higher-order modes (\ie hyperbolicity).
	\comment{tc}{But, na\"ively, I guess this is to be expected, since \eqref{eq:3deps} is explicitly hyperbolic?}
For a bilayer however, there is a higher-order LO mode, associated with out-of-phase oscillation between the two layers, and thus one expects to see a higher-order mode. 
However, it is expected challenging to observe such a mode, as can be anticipated from the blue higher-order mode in Figure~\ref{fig:2}(c), because even for a polariton wavelength of \SI{12}{\nm}, which is very short, the polariton frequency is only a few \si{\per\cm} above the TO frequency, within the damping linewidth of the TO frequency. 
}

>>>>

In the rest of this section, we discuss the relation between the dispersion of an hBN monolayer versus the atomically-thick limit of a thin film of a material with hBN's bulk dielectric function. To aid this discussion, in Figure~\ref{fig:2}(c), we show the dispersion relation of thin films of bulk hBN with film thicknesses of 1, 2, 4, and 8 times the interlayer spacing of bulk hBN, which is roughly \SI{0.33}{\nm}. For these plots, we take hBN to be cleaved such that the optical axis is perpendicular to the plane of the film. The components of the bulk permittivity perpendicular and parallel to the c-axis ($\epsilon_{\perp}$ and $\epsilon_{\parallel}$, respectively; indexed by $\alpha\in\{\perp,\parallel\}$ below) are then given by
\begin{equation}
	\epsilon_{\alpha}(\omega) = \epsilon_{\infty,\alpha}\Bigg(1 + \frac{\omega^2_{\mathrm{LO},\alpha}-\omega^2_{\mathrm{TO},\alpha}}{\omega^2_{\mathrm{TO},\alpha}-\omega^2} \Bigg),
	\label{eq:3deps}
\end{equation}
with $\epsilon_{\infty,\parallel} = \num{2.95}$, $\omega_{\mathrm{TO},\parallel} = \SI{760}{\per\cm}$, and $\omega_{\mathrm{LO},\parallel} = \SI{830}{\per\cm}$; and $\epsilon_{\infty,\perp} = \num{4.87}$, $\omega_{\mathrm{TO},\perp} = \SI{1360}{\per\cm}$, and $\omega_{\mathrm{LO},\perp} = \SI{1614}{\per\cm}$\cite{caldwell2014sub,dai2014tunable}.
Losses are ignored in this discussion altogether. 
In the range between $\omega_{\mathrm{TO}, \alpha}$ and $\omega_{\mathrm{LO}, \alpha}$, the corresponding component of the permittivity is negative, while the other component is positive. This hyperbolicity leads to a dispersion for hBN thin films that have multiple branches at a given frequency, as can be seen in Figure~\ref{fig:2}(c).  This trend persists even when the thickness of the bulk is taken down to a single layer, albeit pushed to high wavevectors. This is in contrast with the true monolayer, where there is only one LO phonon mode. Given that the phonon polariton of 2D is the LO phonon, there can be only one branch of the dispersion. 
\addition{%
The bulk dielectric function of Eq.~\eqref{eq:3deps} fails to capture this removal of higher-order modes (\ie hyperbolicity).
For a bilayer however, there is a higher-order LO mode, associated with out-of-phase oscillation between the two layers, and thus one expects to see a higher-order mode. 
However, it is expected challenging to observe such a mode, as can be anticipated from the blue higher-order mode in Figure~\ref{fig:2}(c), because even for a polariton wavelength of \SI{12}{\nm}, which is very short, the polariton frequency is only a few \si{\per\cm} above the TO frequency, within the damping linewidth of the TO frequency. 
}
